\documentclass[11pt,letterpaper,sans]{moderncv}
\moderncvtheme[grey]{classic}
\usepackage[utf8]{inputenc}

\usepackage[scale=0.75,margin=.75in]{geometry}
\recomputelengths

\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{footmisc}
\usepackage{multibib}
\newcites{pr,conf,post,talk,mthd,code}{Peer Reviewed Journals,%
    Conference Proceedings,%
    Poster Presentations,%
    Invited Talks,%
    Published Methods,%
    Contributions to Open Source Scientific Software}

\makeatletter
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand*\bibliographyitemlabel{\@biblabel{\arabic{enumiv}}}
\makeatother

\title{Curriculum Vitae}
\input{contact}
\extrainfo{Year of Birth: 1987}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2010 -- present}{PhD. Cognitive and Neural Systems}%
    {Boston University}{Boston, MA}{}{Advisor: Jason W. Bohland}
\cventry{2009}{BS. Mathematics}{University of Tulsa}{Tulsa, OK}{}{}
\cventry{2009}{BCS. Computer Science}{University of Tulsa}{Tulsa, OK}{}{}

\section{Additional Research Experience}
\cventry{2005 -- 2008}{Undergraduate researcher}{University of Tulsa}%
    {Tulsa, OK}{}%
    {Operating systems security. Network traffic analysis. Advisor: John Hale}

\section{Professional Employment}
\cventry{2009 -- 2010}{Bioinformatics programmer}{University of Tulsa}%
    {Tulsa, OK}{}{InSilico Research Group: PySNPRank, PyGAIN, Bioinformatics format converters}
\cventry{2009 -- 2010}{Neuroinformatics intern}%
    {Laureate Institute for Brain Research}{Tulsa, OK}{}%
    {XNAT deployment, HIPAA compliance, Asset tracker}
\cventry{Summer 2008}{Intern}{True Digital Security}{Tulsa, OK}{}%
    {High bandwidth traffic shaping, Transparent emergency data destruction}
\cventry{Summer 2007}{Intern}{Meketrex Technologies, Inc.}{Tulsa, OK}{}%
    {Technical copywriting}

\section{Teaching Experience}
\cventry{2008-2009}{Tutor}{University College Cork}{Cork}{Ireland}%
    {CS 4620/4621 Functional Programming. Professor: Joseph Manning}
\cventry{2007-2008}{Teaching assistant}{University of Tulsa}{Tulsa}{OK}%
    {MATH 1083 Contemporary Mathematics. Professor: Janica Edmonds}

\section{Awards and Fellowships}
\cvline{2011 -- 2016}{Research Assistantship,
                      CELEST NSF Science of Learning Center}
\cvline{Nov. 2014}{CompNet Travel Award to Society for Neuroscience Conference}
\cvline{Nov. 2012}{CompNet Travel Award to Society for Neuroscience Conference}
%\cventry{2011 -- 2016}{Research Assistantship}
%    {CELEST, a National Science Foundation Science of Learning Center}{NSF SMA-0835976}
%    {P.I. Shinn-Cunningham}{}
%\cventry{Nov. 2014}{Travel Award}{Boston University Center for Computational
%                    Neuroscience \& Neural Technology}{}{}{}
%\cventry{Nov. 2012}{Travel Award}{Boston University Center for Computational
%                    Neuroscience \& Neural Technology}{}{}{}
\cvline{2010 -- 2011}{Dean's Fellowship for Graduate Study, Boston University}
\cvline{2005 -- 2009}{Presidential Scholarship, University of Tulsa}
\cvline{2006 -- 2008}{Tulsa Undergraduate Research Challenge Program,
                      University of Tulsa}
\cvline{2007}{Barry M. Goldwater Scholarship}
%\cventry{2010 -- 2011}{Dean's Fellowship for Graduate Study}{Boston University}
%    {}{}{}
%\cventry{2007}{Goldwater Scholarship}
%    {Barry M. Goldwater Scholarship and Excellence in Education Program}{}{}{}

\section{Technical Expertise}
\cvline{}{Data analysis, functional magnetic resonance imaging,
    biological modeling, neural networks, neuroinformatics,
    digital signal processing, speech analysis, pattern recognition,
    software engineering, computer security, system administration,
    database management.}
\subsection{Technologies}
\cvline{Scientific}{
    FreeSurfer/FsFast, FSL, AFNI,   % fMRI
    NiPype, PyMVPA,                 % fMRI/Python
    scikit-learn, PsychoPy,         % Scientific Python
    PRAAT}                          % Miscellaneous
\cvline{Cluster computing}{Load Sharing Facility (LSF),
                           Oracle/Sun Grid Engine (SGE),
                           Andrew File System (AFS)}
\cvline{Web}{HTML/CSS, JavaScript, JQuery, Python/Django, Perl/CGI, PHP, WSGI}
\cvline{Version control}{git (GitHub, git-annex), subversion, CVS}
%\cvline{Administration}{nginx, Apache, GitLab, gitolite/git-annex}

\subsection{Programming Languages}
\cvline{Proficient}{Python 2/3, MATLAB, C, Perl, Shell}
\cvline{Competent}{Haskell, \LaTeX, Java, Mathematica}
\cvline{Familiar}{R, JavaScript, PHP, Common LISP}

\nocitepr{Markiewicz2016}
\nociteconf{Louthan2009,Roberts2010}
\nocitetalk{Johnson2013,Johnson2014,Markiewicz2016b}
\nocitepost{JohnsonYazdanbakhsh2012,JohnsonBohland2012,JohnsonBohland2014a,
            JohnsonBohland2014b,Markiewicz2015,Markiewicz2016a}
\nocitemthd{philips-cdas,you2015}
\nocitecode{PyMVPA2_4_1,nipype0_12_0,PySurfer0_6,nibabel2_1_0}
\section{Publications}
\bibliographystylepr{cvbib}
\bibliographypr{self}
\bibliographystyleconf{cvbib}
\bibliographyconf{self}
\section{Presentations}
\bibliographystyletalk{cvbib}
\bibliographytalk{self}
\footnotetext[2]{Presenter, when not first author}
\bibliographystylepost{cvbib}
\bibliographypost{self}
\section{Software}
\bibliographystylemthd{cvbib}
\bibliographymthd{self}
\bibliographystylecode{cvbib}
\bibliographycode{self}

\section{Service/Leadership}
\cventry{2015}{Co-organizer}{7th Annual Inter-Science of Learning Conference}{La Jolla, CA}{}{}
\cventry{2014 -- present}{Student member}{CompNet Outreach and Meeting Initiatives Committee}{Boston University}{}{}
\cventry{2013 -- 2014}{President}{Computational Neuroscience Student Organization}{Boston University}{}{}
\cventry{2013}{Co-organizer}{5th Annual Inter-Science of Learning Conference}{Philadelphia, PA}{}{}

\end{document}
